Test plot_tax_bar()
===================

## Import and clean data

```{r}
# Import Data

library(tidyverse)
theme_set(theme_bw())
library(phyloseq)
devtools::load_all('~/Projects/Mine/aftersl1p/')

load('~/Projects/Mine/aftersl1p/benchmark/data.RData')

seqs = rownames(asv_tab)
all(seqs == rownames(tax_tab))
rownames(asv_tab) = rownames(tax_tab) = NULL

rownames(map_tab) = map_tab$SampleID

setdiff(colnames(asv_tab), rownames(map_tab))
asv_tab = as.matrix(asv_tab)
tax_tab = as.matrix(tax_tab)
dat = phyloseq(otu_table(asv_tab, taxa_are_rows = TRUE),
               tax_table(tax_tab),
               sample_data(map_tab))

# Clean Data
dat
dat = prop_tax_down(dat, indic = FALSE)
dat_rel = transform_sample_counts(dat, function(x) x/sum(x))
keep = taxa_sums(dat)/nsamples(dat) >= 100
dat_filt = prune_taxa(keep, dat)
dat_rel_filt = prune_taxa(keep, dat_rel)
```

## Taxa Bar Charts

* ~~All taxonomic ranks~~
* ~~leglen options:~~
    * ~~NULL~~
    * ~~&gt; n_taxa~~
    * ~~0 &lt; leglen < n_taxa~~
    * ~~0~~
    * ~~< 0~~
    * ~~not a number~~
* legloc options:
    * ~~top~~
    * ~~bottom~~
    * ~~right~~
    * ~~left~~
    * ~~none~~
    * ~~bad~~
* provide own colour vector
    * ~~named (good)~~
    * ~~named (bad)~~
    * ~~named (too short)~~
    * ~~unnamed (long enough)~~
    * ~~unnamed (not long enough)~~
* ~~rotate ticks~~
* ~~means~~

### All taxonomic ranks

#### Kingdom

```{r}
king_df = make_phy_df(dat_rel_filt, 'Kingdom', prop = FALSE)
king_plt = plot_tax_bar(king_df, 'Kingdom', sample = 'SampleID')
king_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/king_plt.pdf',
       width = 10, height = 5)
```

#### Phylum

```{r}
phy_df = make_phy_df(dat_rel_filt, 'Phylum', prop = FALSE)
phy_plt = plot_tax_bar(phy_df, 'Phylum', sample = 'SampleID')
phy_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/phy_plt.pdf',
       width = 10, height = 5)

plot_tax_bar(phy_df, 'Kingdom', sample = 'SampleID')
```

#### Class

```{r}
class_df = make_phy_df(dat_rel_filt, 'Class', prop = FALSE)
class_plt = plot_tax_bar(class_df, 'Class', sample = 'SampleID')
class_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/class_plt.pdf',
       width = 10, height = 5)
plot_tax_bar(class_df, 'Phylum', sample = 'SampleID')
plot_tax_bar(class_df, 'Kingdom', sample = 'SampleID')
```

#### Order

```{r}
ord_df = make_phy_df(dat_rel_filt, 'Order', prop = FALSE)
ord_plt = plot_tax_bar(ord_df, 'Order', sample = 'SampleID')
ord_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/ord_plt.pdf',
       width = 10, height = 5)
plot_tax_bar(ord_df, 'Class', sample = 'SampleID')
plot_tax_bar(ord_df, 'Phylum', sample = 'SampleID')
plot_tax_bar(ord_df, 'Kingdom', sample = 'SampleID')
```

#### Family

```{r}
fam_df = make_phy_df(dat_rel_filt, 'Family', prop = FALSE)
fam_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID')
fam_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/fam_plt.pdf',
       width = 10, height = 5)
plot_tax_bar(fam_df, 'Order', sample = 'SampleID')
plot_tax_bar(fam_df, 'Class', sample = 'SampleID')
plot_tax_bar(fam_df, 'Phylum', sample = 'SampleID')
plot_tax_bar(fam_df, 'Kingdom', sample = 'SampleID')
```

#### Genus

```{r}
gen_df = make_phy_df(dat_rel_filt, 'Genus', prop = FALSE)
gen_plt = plot_tax_bar(gen_df, 'Genus', sample = 'SampleID')
gen_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/gen_plt.pdf',
       width = 10, height = 5)
plot_tax_bar(gen_df, 'Family', sample = 'SampleID')
plot_tax_bar(gen_df, 'Order', sample = 'SampleID')
plot_tax_bar(gen_df, 'Class', sample = 'SampleID')
plot_tax_bar(gen_df, 'Phylum', sample = 'SampleID')
plot_tax_bar(gen_df, 'Kingdom', sample = 'SampleID')
```

#### Species

```{r}
spec_df = make_phy_df(dat_rel_filt, 'Species', prop = FALSE)
spec_plt = plot_tax_bar(spec_df, 'Species', sample = 'SampleID')
spec_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/spec_plt.pdf',
       width = 10, height = 5)
plot_tax_bar(spec_df, 'Genus', sample = 'SampleID')
plot_tax_bar(spec_df, 'Family', sample = 'SampleID')
plot_tax_bar(spec_df, 'Order', sample = 'SampleID')
plot_tax_bar(spec_df, 'Class', sample = 'SampleID')
plot_tax_bar(spec_df, 'Phylum', sample = 'SampleID')
plot_tax_bar(spec_df, 'Kingdom', sample = 'SampleID')
```


### Leglen Options

#### NULL

```{r}
null_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', leglen = NULL)
null_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/null_plt.pdf',
       width = 10, height = 5)
```

#### > n_taxa

```{r}
too_big_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', 
                           leglen = n_distinct(fam_df$Family) + 2)
too_big_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/too_big_plt.pdf',
       width = 10, height = 5)
```

#### 0 < leglen < n_taxa

```{r}
sml_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', 
                           leglen = round(n_distinct(fam_df$Family)/2))
sml_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/sml_plt.pdf',
       width = 10, height = 5)
```

#### 0

```{r}
zero_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', 
                           leglen = 0)
zero_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/zero_plt.pdf',
       width = 10, height = 5)
```

#### < 0

```{r}
ltz_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', 
                           leglen = -1)
ltz_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/ltz_plt.pdf',
       width = 10, height = 5)
```

#### not a number

This raises an error. Test is via `testthat`


### Legloc Options

#### Top

```{r}
top_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', leglen = 10,
                       legloc = 'top')
top_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/top_plt.pdf',
       width = 10, height = 5)
```

#### Bottom

```{r}
bot_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', leglen = 10,
                       legloc = 'bottom')
bot_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/bot_plt.pdf',
       width = 10, height = 5)
```

#### Right

```{r}
right_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', leglen = 10,
                       legloc = 'right')
right_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/right_plt.pdf',
       width = 10, height = 5)
```

#### Left

```{r}
left_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', leglen = 10,
                       legloc = 'left')
left_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/left_plt.pdf',
       width = 10, height = 5)
```

#### None

```{r}
none_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', leglen = 10,
                       legloc = 'none')
none_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/none_plt.pdf',
       width = 10, height = 5)
```

#### Bad

```{r}
bad_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', leglen = 10,
                       legloc = 3)
bad_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/bad_plt.pdf',
       width = 10, height = 5)
```

### Colour Vectors

```{r}
cols = c("#E41A1C","#377EB8","#4DAF4A","#984EA3","#FF7F00","#FFFF33","#A65628",
         "#F781BF")
```

#### Named (good)

```{r}
nmcols = cols
names(nmcols) = c('Other',
                  rev(levels(class_df$Class)[-1]))
nm_gd_plt = plot_tax_bar(class_df, 'Class', colours = nmcols, 
                         sample = 'SampleID')
nm_gd_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/nm_gd_plt.pdf',
       width = 10, height = 5)
```

#### Named (bad)

This raises an error. Test is via `testthat`.

#### Named (too short)

```{r}
nmbd_col_plt = plot_tax_bar(class_df, 'Class', colours = nmcols[1:3],
                            sample = 'SampleID')
nmbd_col_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/nmbd_col_plt.pdf',
       width = 10, height = 5)
```


#### Unnamed (long enough)

```{r}
un_col_plt = plot_tax_bar(class_df, 'Class', colours = cols, 
                          sample = 'SampleID')
un_col_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/un_col_plt.pdf',
       width = 10, height = 5)
```

#### Unnamed (not long enough)

```{r}
unbd_col_plt = plot_tax_bar(class_df, 'Class', colours = cols[1:3], 
                          sample = 'SampleID')
unbd_col_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/unbd_col_plt.pdf',
       width = 10, height = 5)
```

### Rotate ticks

```{r}
rot_plt = plot_tax_bar(fam_df, 'Family', sample = 'SampleID', r_ticks = TRUE)
rot_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/rot_plt.pdf',
       width = 10, height = 5)
```

### Means

#### Means (good)

```{r}
mn_plt = plot_tax_bar(fam_df, 'Family', sample = 'Source', means = TRUE)
mn_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/mn_plt.pdf',
       width = 10, height = 5)
```

#### Means (good, different ns)

```{r}
mn_dn_plt = plot_tax_bar(filter(fam_df, SampleID != 'SHCM34'), 'Family',
                         sample = 'Source', means = TRUE)
mn_dn_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/mn_dn_plt.pdf',
       width = 10, height = 5)
```


#### Means (forget)

```{r}
mn_frgt_plt = plot_tax_bar(fam_df, 'Family', sample = 'Source')
mn_frgt_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/mn_frgt_plt.pdf',
       width = 10, height = 5)
```

#### Means (forget, different ns)

```{r}
mn_dn_frgt_plt = plot_tax_bar(filter(fam_df, SampleID != 'SHCM34'), 'Family',
                              sample = 'Source')
mn_dn_frgt_plt
ggsave('~/Projects/Mine/aftersl1p/benchmark/mn_dn_frgt_plt.pdf',
       width = 10, height = 5)
```

