Test plot_read_depth()
======================

## Import and clean data

```{r}
# Import Data

library(tidyverse)
theme_set(theme_bw())
library(phyloseq)
devtools::load_all()

load('~/Projects/Mine/aftersl1p/benchmark/data.RData')

seqs = rownames(asv_tab)
all(seqs == rownames(tax_tab))
rownames(asv_tab) = rownames(tax_tab) = NULL
head(map_tab)
map_tab = (map_tab
           %>% mutate(ContVar = c(13.6, 8.3, 2.8, 15.5, 10, 6.6, 13.0, 11.5)))
rownames(map_tab) = map_tab$SampleID

setdiff(colnames(asv_tab), rownames(map_tab))
asv_tab = as.matrix(asv_tab)
tax_tab = as.matrix(tax_tab)
dat = phyloseq(otu_table(asv_tab, taxa_are_rows = TRUE),
               tax_table(tax_tab),
               sample_data(map_tab))

# Clean Data
dat
dat = prop_tax_down(dat, indic = FALSE)
dat_rel = transform_sample_counts(dat, function(x) x/sum(x))
keep = taxa_sums(dat)/nsamples(dat) >= 100
dat_filt = prune_taxa(keep, dat)
dat_rel_filt = prune_taxa(keep, dat_rel)

col_vect = c("#E41A1C","#377EB8","#4DAF4A","#984EA3","#FF7F00", 'dodgerblue2',
             'goldenrod3', 'pink')
```



## Tests

### All Defaults

```{r}
plt_read_depth(dat_filt)
```

### xvar

```{r}
plt_read_depth(dat_filt, xvar = 'Source')
```

### cvar continuous, colour default

```{r}
plt_read_depth(dat_filt, cvar = 'ContVar')
```

### cvar categorical, colour default

#### with xvar

```{r}
plt_read_depth(dat_filt, cvar = 'Source', xvar = 'SampleID')
plt_read_depth(dat_filt, cvar = 'Source', xvar = 'Source')
```

#### without xvar

```{r}
plt_read_depth(dat_filt, cvar = 'SampleID')
```


### 1 colour specified, no cvar

```{r}
plt_read_depth(dat_filt, clrs = col_vect[1])
```

### >1 colour specified, no cvar

```{r}
devtools::load_all()
plt_read_depth(dat_filt, clrs = col_vect)
```

### cvar continuous, bad colours

Raises an error. See `testthat` tests

### cvar continuous, high and low

```{r}
col_hl = col_vect[1:2]
names(col_hl) = c('low','high')
col_hl 
plt_read_depth(dat_filt, cvar = 'ContVar', clrs = col_hl)
```

### cvar categorical, unnamed colour vector

```{r}
devtools::load_all()
plt_read_depth(dat_filt, cvar = 'SampleID', clrs = col_vect)
```

### cvar categorical, bad colour vector names

### cvar categorical, names colour vector
